Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-06-11 manuscript/manuscript.Rmd
updates ms with new climate change figure

```{r figure_2, dependson="plot-options", fig.cap="Proportional change in species' mean cover caused by a 1% increase in observed precipitation, temperature, or both as predicted by the individual-based IPM and the aggregate-based QBM. Note that the change for POSE due to a precipitation increase predicted by the QBM is almost zero and so does not show up in the figure. Labels on x-axis refer to: 'ppt' = 1% increase in mean precipitation; 'temp' = 1% increase in mean temperature; 'ppt + temp' = 1% increase in mean precipitation and mean temperature.", fig.width=8.5, fig.height=3, cache=FALSE, results='hide'}
qbm_diffs <- readRDS("../montana/quadBM/simulations/results/qbm_climatesims_logdiffs.RDS")
qbm_diffs$type <- rep("QBM", nrow(qbm_diffs))
ipm_diffs <- readRDS("../montana/ipm/simulations/results/ipm_climatesims_logdiffs.RDS")
ipm_diffs$type <- rep("IPM", nrow(ipm_diffs))

diff_df <- rbind(qbm_diffs, ipm_diffs)

myCols2 <- c("grey45", "#277BA8", "#7ABBBD", "#AED77A")
dgd = position_dodge(width = 0.60)
ggplot(diff_df)+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_errorbar(aes(x=variable, ymin=lo_cover, ymax=up_cover, group=type),
                position=dgd, width=0.25, color="grey45")+
  geom_point(aes(x=variable, y=med_cover, shape=type),
             position=dgd, size=5, color="white")+
  geom_point(aes(x=variable, y=med_cover, shape=type),
             position=dgd, size=3)+
  scale_shape_manual(values = c(19,17), name="Model type")+
  xlab("Climatic change")+
  ylab("Proportional change in percent cover")+
  facet_grid(.~species)+
  scale_x_discrete(labels=c("ppt", "temp", "ppt + tmp"))+
  theme_bw()
```

>>>>

```{r figure_2, dependson="plot-options", fig.cap="Proportional change in species' mean cover caused by a 1% increase in observed precipitation, temperature, or both as predicted by the individual-based IPM and the aggregate-based QBM. Note that the change for POSE due to a precipitation increase predicted by the QBM is almost zero and so does not show up in the figure. Labels on x-axis refer to: 'ppt' = 1% increase in mean precipitation; 'temp' = 1% increase in mean temperature; 'ppt + temp' = 1% increase in mean precipitation and mean temperature.", fig.width=8.5, fig.height=3, cache=FALSE, results='hide'}
ipm_diffs <- readRDS("../montana/ipm/simulations/results/ipm_climatesims_logdiffs.RDS")
ipm_diffs$model <- rep("IPM", nrow(ipm_diffs))
ipm_diffs$type <- rep("paramunc", nrow(ipm_diffs))
ipm_diffs2 <- readRDS("../montana/ipm/simulations/results/ipm_climatesims_logdiffs_mean.RDS")
ipm_diffs2$model <- rep("IPM", nrow(ipm_diffs))
ipm_diffs2$type <- rep("parammean", nrow(ipm_diffs))
ipm_diffs$med_cover <- ipm_diffs2$med_cover
ipm_diffs <- rbind(ipm_diffs, ipm_diffs2)

ggplot(ipm_diffs)+
  geom_hline(aes(yintercept=0), linetype=2)+
  geom_errorbar(aes(x=species, ymin=lo_cover, ymax=up_cover, group=variable),
                position=dgd, width=0.25, color="grey45")+
  geom_point(aes(x=species, y=med_cover, shape=variable),
             position=dgd, size=5, color="white")+
  geom_point(aes(x=species, y=med_cover, shape=variable),
             position=dgd, size=3)+
#   scale_shape_manual(values = c(19,17), name="Model type")+
  xlab("Climatic change")+
  ylab("Proportional change in percent cover")+
  facet_wrap("type",scales = "free")+
#   scale_x_discrete(labels=c("ppt", "temp", "ppt + tmp"))+
  theme_bw()

# qbm_diffs <- readRDS("../montana/quadBM/simulations/results/qbm_climatesims_logdiffs.RDS")
# qbm_diffs$type <- rep("QBM", nrow(qbm_diffs))
# ipm_diffs <- readRDS("../montana/ipm/simulations/results/ipm_climatesims_logdiffs.RDS")
# ipm_diffs$type <- rep("IPM", nrow(ipm_diffs))
# 
# diff_df <- rbind(qbm_diffs, ipm_diffs)
# 
# myCols2 <- c("grey45", "#277BA8", "#7ABBBD", "#AED77A")
# dgd = position_dodge(width = 0.60)
# ggplot(diff_df)+
#   geom_hline(aes(yintercept=0), linetype=2)+
#   geom_errorbar(aes(x=variable, ymin=lo_cover, ymax=up_cover, group=type),
#                 position=dgd, width=0.25, color="grey45")+
#   geom_point(aes(x=variable, y=med_cover, shape=type),
#              position=dgd, size=5, color="white")+
#   geom_point(aes(x=variable, y=med_cover, shape=type),
#              position=dgd, size=3)+
#   scale_shape_manual(values = c(19,17), name="Model type")+
#   xlab("Climatic change")+
#   ylab("Proportional change in percent cover")+
#   facet_grid(.~species)+
#   scale_x_discrete(labels=c("ppt", "temp", "ppt + tmp"))+
#   theme_bw()
```
